A Detection of the Environmental Dependence of the Stellar Halos of Massive Central Galaxies

### 2017-03-24 draft/ms_v8.tex
Close to finishe

    In this paper, we take advantage of new high-resolution (median 
    FWHM$\sim 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program (SSP; \citealt{HSCDR1; will be referred as the HSC survey} to revisit the 
    question of the environmental dependence in the mass-size relation. 
    The goal of this paper is to compare the \mden{} profiles and structural scaling 
    relations of massive central galaxies in both low and high mass dark matter halos. 
    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample ($\sim 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using $\sim 100$ square degree of data from the 
    HSC wide layer.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) and 
          \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples. 
          Orange and red correspond to \rbcg{} and grey and black correspond to \nbcg{}. 
          The \mtot{}-matched samples are shown on the left and the \minn{}-matched 
          samples are shown on the right. 
          Thin lines show the \mden{} profile for individual galaxies. 
          Thick lines with shaded regions show the median profile for each sample with 
          uncertainties given by the shaded region. 
          The bottom panel highlights the differences between the two median profiles 
          (brown solid line and shaded region). 
          To test the significance of the differential profile, we perform statistical
          tests by comparing the median profiles of two random groups that are drawn 
          from the mixed sample, and have the same sizes with the matched \rbcg{} and
          \nbcg{} ones. 
          Repeating this process 5000 times, the median (black solid line), 1-$\sigma$ 
          (dark-grey shaded region) and 3-$\sigma$ (light-grey shaded region) ranges
          of these random differential profiles are shown on the bottom panel.}
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients indicating 
    gradients in \m2l{} \alexie{xxx} (e.g.\ \citealt{LaBarbera2012}; 
    \citealt{DSouza2015}). 
    These color gradients are shallow and smooth out to a few times of the effective 
    radius and color gradients at the outskirts are not yet well quantified. 
    More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
    our results will be robust as long as there is \emph{no significant difference in the 
    average color gradient between the two samples}. 
    We have confirmed that this is indeed the case and this will be discussed in Section 
    \ref{ssec:ell_color}.

@@

    Compared to the much discussed "mass-size" relation, the \mden{} profiles that we 
    have derived capture the full information about the structural properties of 
    massive galaxies. 
    We argue that by studying the shapes of these galaxy profiles directly, we can 
    by-pass outstanding questions about how to accurately define and measure the 
    "sizes" and "masses" of these massive galaxies. 
    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
    profiles along with their uncertainties are derived using bootstrap resampling 
    method} of massive galaxies at $0.3 < z < 0.5$ in three \mtot{} bins\footnote{Here 
    we ignore a small population of massive satellites \alexie{xxxx} in \redm{} clusters 
    we excluded from our sample. 
    The sample is clearly not complete in the lowest \mtot{} bin, but its median \mden{}
    profile is still useful to show the overall trend and to compare with previous 
    observations}. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc 
    \textbf{individually}. 
    These median \mden{} profiles have moderate differences in the inner region, 
    but show significant differences in the outskirts with more massive galaxies 
    showing more prominent stellar envelopes. 
    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
    profiles (e.g.\ \citealt{Lauer07}). 
    But in the outskirts, the structure of these galaxies clearly does \textbf{NOT} 
    response to the increase of stellar mass in a self-similar way.
    As mentioned earlier, some of the \mden{} profiles show signs of unphysical 
    truncation and fluctuation related to inaccurate sky subtraction.  
    We exclude the profiles outside 100 kpc, even though the median \mden{} 
    profiles for the two more massive bins behave reasonably out to $\sim 200$ kpc.

    The right panel of Fig~\ref{fig:avg_prof} compares our median profiles with a few
    past works.
    So far, the surface brightness profiles of massive galaxies out to such large 
    radii was mostly derived via image stacking technique that suffers from several 
    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
    available.
    \citep{Huang2013a} derived \mden{} profiles for a small sample of very 
    nearby ellipticals (within 100 Mpc; median \logms{}$\sim 11.3$ based on shallower 
    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}) that are 
    only affected by seeing within $r < 1$ kpc. 
    This median \mden{} profile qualitatively agrees with the one for the lowest 
    \mtot{} bin in the inner region, but shows a slightly more prominent outer 
    envelope at $r > 15$ kpc. 
    While the small size of the CGS sample ($\sim 30$) and differences in the
    measurements of \mstar{} could explain this difference, it may also correspond 
    to evidence for build-up in the outskirts of massive galaxies from $z\sim 0.4$ 
    to $z=0$. 
    CGS images are deeper than SDSS images in the $r$-band, but the median 
    profile from \citep{Huang2013a} still only reaches $\sim 50$ kpc for $z\sim 0$ 
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z\sim 0.4$ galaxies out to at least 100 kpc.

    \citet{Patel2013} extracted a median \mden{} profile of massive ETGs at 
    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
    These galaxies are selected at a constant cumulative number density and are 
    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
    The median \mstar{} of the \citet{Patel2013} sample is $\sim 10^{11.2} M_{\odot}$, 
    but the shallower imaging depth and the differences in SED fitting 
    assumptions\footnote{\citep{Patel2013} uses the BC03 SSP model, which show an 
    average -0.1 dex difference with the FSPS one based on our tests.}
    can make them comparable to our galaxies in the lowest \mtot{} bin, and the 
    comparison of \mden{} profiles does confirm that. 
    The superb resolution of the \textit{HST}/ACS image means that the profile in
    \citet{Patel2013} is unaffected by the seeing even down to 1 kpc. 
    The good agreement between our profile and the one derived from HST image 
    shows that our profiles are robust at $r > 3$ kpc and that we can accurately 
    measure \minn{}.

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (\citealt{Cooper10}). 
    Despite the poorer resolution, the simulated \mden{} profile is already quite 
    similar to the median \mden{} profile for the $11.6 <$ \logmtot{} $< 11.8$ bin 
    within 40 kpc. 
    However, compared with our data, this simulation predicts stellar envelope that
    are too prominent at this halo mass. 
    This types of comparisons between our HSC data and predictions from simulations 
    will help to fine-tune simulations and to also investigate the main physical 
    mechanisms that drive the assembly of massive galaxies and the build up of 
    stellar envelopes.

    Table 1 provides tabulated values for the median profiles that are displayed 
    in Fig~\ref{fig:avg_prof}. 
    These profiles are also available  
    \href{https://github.com/dr-guangtou/hsc_redbcg/tree/master/profiles}{here}:
    {\url{https://github.com/dr_guangtou/hsc_redbcg/tree/master/profiles/}}.

@@

%% ------------------------------------------------------------------------------------ %% 
\subsubsection{Environmental Dependence of the \mden{} Profiles}
    \label{sssec:sbp_mtot}

    Finally, we will look into the environmental dependence of structures in massive 
    galaxies using the \mden{} profiles of the \rbcg{} and \nbcg{} samples that are 
    carefully matched in \mstar{} and redshift using KDTree algorithm. 
    We discuss the details and quality of the matching procedure in 
    Appendix~\ref{app:match} (see Fig~\ref{fig:match}. 
    The matched redshift distributions within $0.3 < z < 0.5$ ensures the \mden{} 
    profiles from both samples are impacted by seeing and background at similar level. 
    As for the \mstar{}, we choose to match using two physically meaning definitions.

    \begin{itemize}
        \item \mtot{} as the proxy of the ``total'' \mstar{} that include the stellar 
            envelope.  As mentioned earlier, we match the two samples within 
            $11.6 < $\logmtot{}$<11.9$ (median \logmtot{}$\sim 11.74$).
            For the 45 \rbcg{} galaxies, we have 229 unique \nbcg{} galaxies in the 
            matched sample.
            Within this \mtot{} range, 100 kpc equals to 5-8 times of the effective 
            radius, so should enclose most their \mstar{}. 
            In practice, this choice also reflects the radius range that we can safely 
            measure \mden{} profile given the depth of the image and the accuracy of 
            background subtraction.

        \item \minn{} as the proxy of the \mstar{} of the ``in-situ'' component.
            This is motivated and supported by recent observations and simulations, 
            and we will discuss more about this assumption in 
            Section~\ref{sec:discussion}.
            We match the two samples within $11.2 < $\logminn{}$ < 11.6$ 
            (median \logminn{}$\sim 11.36$).
            For 56 galaxies in this \rbcg{} sample, we achieve excellent matches
            using 375 \nbcg{} galaxies.
    \end{itemize}

    We show the comparison of the \mtot{}-matched (\minn{}-matched) samples in the 
    left (right) panel of Fig~\ref{fig:prof_1}.

    For the \mtot{}-matched comparison, it is easy to see that the \mden{}
    profiles of \rbcg{} and \nbcg{} galaxies \textbf{greatly overlap with each 
    other over the entire radius range}, which partially explains the difficulties in 
    confirming any environmental dependence of structure in earlier works.
    Although the central galaxies from more massive halos do not form a unique 
    population in term of their structures comparing with the ones in less massive
    halos at similar \mtot{}, we can still spot interesting differences in their 
    median profiles: the \rbcg{} galaxy on average has slightly more flattened inner 
    profile and more significant outer stellar envelope than the \nbcg{} one.
    We highlight these subtle differences in the bottom panel using the difference 
    between the two median profiles and its uncertainty. 
    Given the noticeable uncertainties of \mtot{} and $\lambda$, along with the 
    small size of the current \rbcg{} sample, we perform statistical test to confirm 
    the robustness of the result \footnote{We mix the $N_{\mathrm{r}}$ \rbcg{} 
    galaxies and the $N_{\mathrm{n}}$ \mtot{}-matched \nbcg{} ones together, then 
    randomly draw $N_{\mathrm{r}}$ galaxies with putting-back, compute the difference 
    between the median profile of this sample and the \nbcg{} sample. 
    After repeating this process 2000 times, we can evaluate the possibility that 
    the systematic differences in median \mden{} profiles can be reproduced by random 
    selection of massive galaxies.}
    In both inner and outer regions, we conclude the systematic differences in 
    median \mden{} profiles are significant and robust.
    Interestingly, the median profiles for \rbcg{} and \nbcg{} cross each other 
    at $\sim 15$-20 kpc, quite close to the expected $R_{\mathrm{e}}$ for ETGs 
    this massive. 
    In Appendix~\ref{app:robust}, we further prove the robustness of this 
    interesting result by showing that it is not affected by the range of redshift,
    range of richness, and the choice of proxy for ``total'' \mstar{} 
    (see Fig~\ref{fig:prof_3}). 
    We also explore the possible \mtot{}-dependence of this structural difference 
    despite the limitation of \mstar{}-completeness and small sample size
    (see Fig~\ref{fig:prof_2}) in Appendix~\ref{app:robust}.
    Although the systematic differences are very similar in different \mtot{} bins, 
    we do find some hints that suggest the environmental dependence becomes more 
    significant at the more massive end.  
    This evidence could have intriguing implication in the assembly history of 
    massive galaxies, and is worth more investigations with larger and more completed 
    sample later.

    \textbf{All these tests confirm that we robustly detect subtle, but systematic 
    \mhalo{}-dependence (environmental dependence) of structure in massive, 
    central galaxies} that seems to be consistent with the expectation of more frequent 
    (minor) mergers in denser environment. 
    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
    a lot, but are efficient in depositing stellar mass onto the outer envelope
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).

%% ------------------------------------------------------------------------------------ %% 
    Meanwhile, the subtlety of this environmental dependence for \mtot{}-matched 
    samples seems to suggest that environment plays a secondary role in shaping 
    the structure of galaxies at fixed total stellar mass, and it encourages us to find
    another interesting angle.  
    For instance, for massive galaxies that formed similar amount of stars through 
    intensive star formation at high redshift, how the environments affect their mass 
    assembly history in the second phase? 
    We attempt to investigate this question through comparing the \mden{} profiles of 
    the \minn{}-matched \rbcg{} and \nbcg{} galaxies (right side of 
    Fig~\ref{fig:prof_1}).
    Assuming we are now comparing the average structures of massive galaxies that share 
    similar \mstar{} in the ``in-situ'' component, we start to see the environmental 
    dependence much more clearly without any statistical test.     
    The median \mden{} profiles of \rbcg{} and \nbcg{} galaxies are quite similar in 
    the inner 5-10 kpc, but the \rbcg{} galaxies clearly show much more prominent
    outer envelope.

    It is also worth noting that \mden{} profiles of massive galaxies have quite uniform
    slope and small scatter inside 10 kpc.  
    In contrast, their outer profiles could have a large range of slopes and much 
    larger scatters than the inner region. 
    It seems to suggest that the inner and outer parts of massive galaxies are shaped 
    by distinctive physical processes, and are affected by their environment at 
    very different level. 
    Given the highly dissipative nature of the ``in-situ'' phase, the similarity of 
    inner profiles is consistent with the idea that processes like wet-merger and 
    star burst often create de~Vaucouleur-like ($n\sim 4$) \mden{} profile
    (e.g. \citealt{Hopkins2008}).
    At the same time, the outer envelope of massive galaxies are predicted to be 
    gradually assembled by non-dissipative mergers, which is a stochastic process and 
    is more affected by the environment.  
    Therefore, it is natural to see larger diversity in the outer profiles of 
    low-$z$ massive galaxies. 
    On average, massive galaxies in more massive halos show shallower outer \mden{} 
    profiles, which is in qualitative agreement with recent simulation
    (e.g. \citealt{Pillepich2014}).
    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
    we show the 3-color images of randomly selected massive central galaxies that 
    have similar \minn{} ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
    but different \mtot{}.   
    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.

    As with the \mtot{}-matched sample, the results are very robust against 
    sample details, definition of ``inner'' \mstar{} and the \minn{} bins. 
    In Appendix~\ref{app:match}, we also show that:
    1) When we match using both \minn{} and \meff{}, we end up with \rbcg{} and \nbcg{} 
    samples with perfectly matched inner median \mden{} profiles, while the different 
    in the outskirt remains the same (see the left figure of Fig~\ref{fig:prof_4}).  
    2) Also, the results will not change even when only a more \mstar{}-complete sample
    (\logmtot{}$> 11.5$) is considered (see the right figure of Fig~\ref{fig:prof_4}).

    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table.1.
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
      \caption{
          Comparisons of the radial profiles of ellipticity and optical colors 
      	  for \mtot{}-matched (\textbf{left figure}) and \minn{}-matched 
      	  (\textbf{right figure}) of \rbcg{} (orange-red) and \nbcg{} (grey-black) samples. 
          The formats are very similar to the figure for \mden{} profile 
          (e.g. right figure of Fig~\ref{fig:prof_1}). 
          On each side, from top to bottom, we show the elliptical profile, and the 
          color profile using $g-r$ and $g-i$ color. 
          Since the individual profile of these properties has very large uncertain in the 
          outskirt, we block the region at large radii where we think the median profiles 
          are still unreliable using a dark, shaded box.
          We also compare these results with previous results based on SDSS images. 
          They are: 
          1) Ellipticity profile of the stacked image of a large sample of red galaxies at 
          $z\sim 0.4$ from \citet{Tal2011} with PSF correction 
          (solid blue line on top panel); 
          2) Ellipticity and $g-r$ color profiles from stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in \citet[][blue dash lines 
          on the top and middle panels]{DSouza2014}; 
          3) average $g-r$ and $g-i$ color profiles for a large sample of nearby 
          elliptical galaxies in \citet[][blue, solid lines on the middle and bottom 
          panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

    In this paper, we take advantage of new high-resolution (median 
    FWHM$\sim 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to revisit the 
    question of the environmental dependence in the mass-size relation. 
    The goal of this paper is to compare the \mden{} profiles and structural scaling 
    relations of massive central galaxies in both low and high mass dark matter halos. 
    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample ($\sim 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using $\sim 100$ square degree of data from the 
    HSC wide layer.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          The left panel corresponds to samples matched by "total" stellar mass 
          (\mtot{}). 
          The right panel corresponds to samples matched by "core-mass" (\minn{}). 
          Orange and red lines correspond to central galaxies living in halos with 
          \logmh{} $\geq 14.2$. 
          Black and grey correspond to central galaxies living in halos with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          The brown line in the bottom panels show the relative difference between 
          two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
          Errors on the difference between the two profiles is computed via bootstrap 
          too. 
          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
          We repeat this process 5000 times.  
          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients indicating 
    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
    \citealt{DSouza2015}). 
    These color gradients are shallow and smooth out to a few times of the effective 
    radius and color gradients at the outskirts are not yet well quantified. 
    More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
    our results will be robust as long as there is \emph{no significant difference in 
    the average color gradient between the two samples}. 
    We have confirmed that this is indeed the case and this will be discussed in 
    Section~\ref{ssec:ell_color}.

@@

    Compared to the much discussed "mass-size" relation, the \mden{} profiles that we 
    have derived capture the full information about the structural properties of 
    massive galaxies. 
    We argue that by studying the shapes of these galaxy profiles directly, we can 
    by-pass outstanding questions about how to accurately define and measure the 
    "sizes" and "masses" of these massive galaxies. 
    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
    profiles along with their uncertainties are derived using bootstrap resampling 
    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
    but its median \mden{} profile is still useful to show the overall trend and to 
    compare with previous work}. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc 
    \textbf{individually}. 
    These median \mden{} profiles have moderate differences in the inner region, 
    but show significant differences in the outskirts with more massive galaxies 
    showing more prominent stellar envelopes. 
    Most of these massive galaxies ($\ge 10^{11.4} M_{\odot}$) are slowly-rotating 
    (e.g.\ \citealt{Cappellari13b}) giant ellipticals with ``boxy'' inner isophotal 
    shapes (e.g.\ \citealt{Kormendy2009}), and slightly flattened inner \mden{} 
    profiles (e.g.\ \citealt{Lauer07}). 
    But in the outskirts, the structure of these galaxies is 
    \emph{clearly not self-similar}. 
    Some of our \mden{} profiles show signs of unphysical truncation and fluctuation 
    related to inaccurate sky subtraction. 
    In this paper, we do not use profiles beyond 100 kpc, even though the median 
    \mden{} profiles for the two most massive bins behave reasonably out to 
    $\sim 200$ kpc.

    Fig~\ref{fig:avg_prof} compares our results with previous work. 
    Most previous studies have relied on stacking techniques to measure surface 
    brightness profiles out to large radii.
    So far, the surface brightness profiles of massive galaxies out to such large 
    radii was mostly derived via image stacking technique that suffers from several 
    systematic issues (e.g. \citealt{Tal2011, DSouza2015}; but also see:
    \citealt{Capaccioli2015}); and the \mden{} profiles are even more rarely 
    available.

    \citep{Huang2013a} derived \mden{} profiles for a small sample of very nearby 
    ellipticals (within 100 Mpc; median \logms{} $\sim 11.3$ based on shallower 
    images) from the Carnegie-Irvine Galaxy Survey (CGS, \citealt{CGS1}). 
    Because this is a very low redshift sample, these profiles are robust to $r=1$ kpc. 
    The \citep{Huang2013a} profiles show good agreement with ours in the region of 
    overlap and out to 50 kpc. 
    CGS images are deeper than SDSS images in the $r$-band, but the median 
    profile from \citep{Huang2013a} still only reaches $\sim 50$ kpc for $z\sim 0$ 
    massive galaxies.
    Meanwhile, our deep HSC images can reliably deliver individual \mden{} profiles 
    for $z\sim 0.4$ galaxies out to at least 100 kpc.

    \citet{Patel2013} extracted a median \mden{} profile of massive ETGs at 
    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
    These galaxies are selected at a constant cumulative number density and are 
    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
    The median \mstar{} of the \citet{Patel2013} sample is $\sim 10^{11.2} M_{\odot}$ 
    which is lower than our lowest mass bin. 
    However, \citep{Patel2013} use the BC03 SSP model which are roughly 0.1 dex 
    lower than our FSPS masses (Appendix~\ref{app:sed}). 
    Furthermore, the \citep{Patel2013} images are shallower than ours meaning 
    that there masses will be lower than ours because of missing light in the 
    outskirts. 
    Given these two considerations, it is reasonable to roughly compare the 
    \citep{Patel2013} profile with the one in our lowest stellar mass bin. 
    The superb resolution of the \textit{HST}/ACS image means that the profile in
    \citet{Patel2013} is unaffected by the seeing even down to 1 kpc. 
    The good agreement between our profile and the one derived from HST image 
    shows that our profiles are robust at $r > 3$ kpc and that we can accurately 
    measure \minn{}.

    Finally, we also compare with the predicted median \mden{} profile of central 
    galaxies in massive halos ($13.5 < \log M_{200,c} < 14.0$) from cosmological 
    simulation where the \mden{} profiles of galaxies are calculated using the 
    particle-tagging technique (\citealt{Cooper10}).

    The simulated \mden{} profile is also affected by limited resolution in the 
    center, but it is already quite similar to the median \mden{} profile for 
    the $11.6 <$ \logmtot{} $< 11.8$ bin within 40 kpc. 
    However, compared with our data, this simulation predicts stellar envelope that
    are too prominent at this halo mass. 
    This types of comparisons between our HSC data and predictions from simulations 
    will help to fine-tune simulations and to also investigate the main physical 
    mechanisms that drive the assembly of massive galaxies and the build up of 
    stellar envelopes.

    Table~1 provides tabulated values for the median profiles that are 
    displayed in Fig~\ref{fig:avg_prof}. 
    These profiles are also available  
    \href{https://github.com/dr-guangtou/hsc_redbcg/tree/master/profiles}{here}:
    {\url{https://github.com/dr_guangtou/hsc_redbcg/tree/master/profiles/}}.

@@

%% ------------------------------------------------------------------------------------ %% 
\subsubsection{Environmental Dependence of the Profiles of Massive Galaxies}
    \label{sssec:sbp_mtot}

    We now ask whether or not galaxies from our sample have \mden{} profiles that 
    depend on \mhalo{} (at fixed \mstar{}). 
    For this, we will build matched samples drawing from \rbcg{} and \nbcg{} that are 
    carefully matched in \mstar{} and redshift using a KDTree algorithm 
    (see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
    By matching the redshift distributions within $0.3 < z < 0.5$, we ensure that the 
    \mden{} profiles from both samples are impacted by seeing and background subtraction 
    at similar levels. 
    To match the two samples by stellar mass, we will use two different methods:

        \item We match the two samples according to \mtot{}. 
            We select galaxies from \rbcg{} with $11.6 < $\logmtot{} $<11.9$ 
            (median \logmtot{} $\sim 11.74$). 
            There are 45 \rbcg{} galaxies in this range. 
            We then match this distribution by drawing galaxies from \nbcg{}. 
            There are 229 unique \nbcg{} galaxies in the matched sample. 
            In this \mtot{} range, 100 kpc corresponds to 5-8 times the effective radius 
            and \mtot{} is a good proxy of total stellar mass.

       \item We match the two samples according to \minn{}. 
           We select galaxies from \rbcg{} with $11.2 < $\logminn{}$ < 11.6$ 
            (median \logminn{}$\sim 11.36$).
            For the 56 galaxies from the \rbcg{} sample, we achieve excellent matches
            in \minn{} and redshift using 375 \nbcg{} galaxies.
            Motivated by recent observations and simulations, we use \minn{} as the 
            proxy of the \mstar{} of the ``in-situ'' component.
            We will discuss more about this assumption in 
            Section~\ref{sec:discussion}.

    \end{itemize}

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the profiles of galaxies at fixed \mtot{} and at fixed 
    \minn{} for our two matched samples, and shows the main results of this paper which 
    is that we find a clear halo mass dependence in the \mden{} profiles of massive 
    galaxies. 
    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the two 
    profiles, $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
    \log(\mu_{\star, \mathrm{cenLowMh}})$, 
    with errors computed via bootstrap resampling. 
    In Appendix~\ref{app:robust}, we present a variety of tests that verify the 
    robustness of these results against different uncertainties.

    There are several important points to be noticed in Fig~\ref{fig:prof_1}. 
    First, when galaxies are matched by \mtot{}, although we detect a robust 
    environmental dependence, it mainly only becomes prominent in the outskirts 
    at $R>50$ kpc. 
    This partially explains the difficulties for previous works to detect this effect
    on shallower images. 
    Second, we find that central galaxies in more massive dark mater halos display 
    more flattened inner profile and more significant outer stellar envelope than 
    the ones living in less massive halos. 
    Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each other 
    at $\sim 15$-20 kpc, the expected $R_{\mathrm{e}}$ for ETGs at this \mtot{}. 
    Finally, such systematic difference in structure may become more significant 
    at very high-mass end. 
    We see evidence of this effect when we compare the $Delta$ profiles in two \mtot{} 
    bins (see Fig~\ref{fig:prof_2} and discussion in 
    Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes somewhat
    incomplete} and when we discuss the relation between \mtot{} and \minn{} for 
    these two samples (see Fig~\ref{fig:scaling_relation}). 
    This potential interesting result and its implication is worth more investigations 
    later.

    Meanwhile, the subtle environmental dependence of \mden{} profiles for the 
    \mtot{}-matched samples suggests that environment does not play the major role in 
    shaping massive galaxies \textbf{at fixed total stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the in-situ component}, how does environment affect their 
    subsequent mass assembly?
    Assuming that the \minn{} is reasonable proxy of in-situ mass, we look into this 
    question by comparing the \mden{} profiles of the \minn{}-matched samples ( 
    Fig~\ref{fig:prof_1}, right).  
    Although the median \mden{} profiles are similar at $r \leq 10$ kpc, the
    central galaxies in more massive halos clearly possess much more prominent outer
    envelope. 
    This result is robust in a series of statistical and systematical tests 
    (see Appendix~\ref{app:robust}.

    At the same time, the uniform slope of the \mden{} profiles within 
    10 kpc is in sharp contrast with the large scatter of the outskirts. 
    It hints that these two regions are shaped by distinctive processes, and may 
    explain their differences in environmental dependency. 
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n\sim 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The stochastic nature of the merging process also helps explain the 
    large scatter in the distributions of outer \mden{} profiles. 
    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
    we show the 3-color images of randomly selected massive central galaxies that 
    have similar \minn{} 
    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
    but different \mtot{}.   
    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.

    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
    (environmental dependence) of structure in massive central galaxies}, which seems 
    to be consistent with the expectation of more frequent (minor) mergers in denser 
    environment. 
    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
    a lot, but are efficient in depositing stars to the outer envelope
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})

    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table~1.
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_discussion_2}
      \caption{
          Radial variations in ellipticity and optical colors for massive galaxies. 
          The format of this figure is similar to the right hand side of 
          Fig~\ref{fig:prof_1}. 
          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
          panels show $g-i$. 
          We compare our results with those from \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z\sim 0.4$ 
          (solid blue line on top panel). 
          We also compare with the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on the middle and bottom panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
    optical colors of massive galaxies vary with radius. 
    We also study whether or these radial trends differ between our various samples. 
    These quantities contain interesting information about the physical processes that 
    shape galaxies, but here we study them mainly with two goals in mind:

        \item To see whether the ellipticity profile depends strongly on environment, 
            and to see whether or not the fact that we use an using average isophotal 
            shape for our our 1-D \mden{} profiles has any impact on our results.

        \item To verify that the average color gradient does not depend strongly on 
            the environment and that is not steep enough to cause a problem with our 
            choice the assumption that it is reasonable to use average \m2l for 
            comparing massive galaxies. 
            We extract color profiles by applying the isophotes in $i$-band to images 
            in other bands in ``forced photometry'' manner.
